---
title: "challenge"
output: bookdown::html_document2
author: "Joana Seguin"
date: '`r Sys.Date()`'
bibliography: my_references.bib
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## First function

Here is my new function:

```{r three}
library(mytestpkg)
followers(3)
```

More Information can be found (need to look this up).

```{r five}
library(mytestpkg)
followers(5)

```

##Wednesday

On Wednesday we started with a challenge to get familiar with work with all this. You can see the result in Figure \@ref(fig:cars) and Table \@ref(tab:tableone) 
Here is my table to practise using markdown files. 

```{r cars, fig.cap= "This plot demonstrates speed and distance of cars of a given dataset", echo=FALSE}
plot(cars, col="blue")
```

In Figure \@ref(fig:cars) you can clearly see that i managed to produce a plot. You can find interesting literature by an author called Cars here: [@madanipour2000social].
If you don't like figures, here is a table with numbers:

```{r tableone, echo=FALSE}
knitr::kable(tail(cars), caption = "My table with random cars")
```

I also created a new function. 
```{r half}
library(mytestpkg)
m <- half(2)
n <- half(5)
o <- half(10)
print(c(m, n, o))
```

Useful for output description:
paste("the value is", x)
glue::glue("the value is", y)

## Thursday
<!-- packrat is for using old package versions (=#packrat::on()), but inconvenience is that you take the packages with you which makes your project very large
-->

```{r}
library(binford)
data(LRB)
knitr::kable(head(LRB))
```

